---
title:  "Clearing the Decks"
author: "Melina Much Ph.D. Candidate"
output: slidy_presentation
---

## Welcome

This is an R focused bootcamp for beginner and intermediate R users. We created this as graduate students to fill a gap that we faced during our time in the program. It is largely meant to bridge the gap between your entrace to the program, and the start of Prof. Levin's statistics sequence.

## Topics

- R, what is it?
- Base, Tidyverse, Packages/Functions
- Project Workflow
- Style Guides

## R, what is it?

-**R** is a language and environment for statistical computing and graphics. It is *free* and *open source*. It is a more powerful version of things like STATA or SPSS.

-**RStudio** is an integrated development environment that works on top of R software. It provides a more user friendly interface to work with R.

-The **“Comprehensive R Archive Network” (CRAN)** is a collection of sites which carry identical material, consisting of the R distribution(s), the contributed extensions, documentation for R, and binaries.

## Base, Tidyverse, Packages/Functions

-**Base R** refers to the basic functions and languages that are present in the software without any further installation.

-Tools designed beyond base R by professors, programmers, and statisticians are called **packages**. They can be freely added to your R to give you tools beyond Base.

-**Tidyverse** is a system of packages for data manipulation, exploration, and visualization that share a common design philosophy of "tidiness." They share syntax styles and have their own style guide. I will encourage learning tidyverse *after* learning base R, as the tidyverse places a strong emphasis on human readability. 

## Project Workflow

1) Set **Project** within a directory that you can easily access 

2) Use style guide to name projects, and *all* folders within that project 

3) Use folders

4) Use **R Markdown** whenever possible

5) Repeat for *every* project

## Version Control 

- We use Github to keep track of all changes made to our code, and make it easy for our group to collaborate and share files. 

- This is an important part of project work flow, because it allows you to revert to previous versions of a project when you make a mistake.

- It also increases transparent research practices in the scientific community, which can help reduce impacts of the reproducibility crisis.

- For our purposes in the Bootcamp, it provides an easy way for you to access all the code for the week at once. 

## Connecting Github

```{r}

library(gitcreds)

#gitcreds_set()

```


## Style Guides

Style guides create conistency across coding groups, and increase the ability of you or someone else to be able to decifer your code later on down the line. 

1) [Tidyverse](https://style.tidyverse.org/)

2) [Google](https://google.github.io/styleguide/Rguide.html)

We will go over tidyverse...why? 

## Tidyverse Styling

**It is so tidy!**

Prioritizes not just reproducibility across coders, but is *arguably* the most human readable. I will show you a few examples in the next slides, but the style guides will mostly come into play when you start writing up your Labs.

## Tidyverse Styling

**File names and object names** use underscores.

*Good*

fit_models.R

utility_functions.R

00_download.R

01_explore.R

...

09_model.R

10_visualize.R

## Tidyverse Styling

*Suboptimal*

fit models.R

foo.r

stuff.r

## Tidyverse Styling

For **Commas and Parenthesis** always put a space after a comma, never before, just like in regular English. Do not put spaces inside or outside parentheses for regular function calls, also like regular English grammar.

*Good*

x[, 1]

mean(x, na.rm = TRUE)

## Tidyverse Styling

*Suboptimal*

x[,1]

x[ ,1]

x[ , 1]

mean (x, na.rm = TRUE)

mean( x, na.rm = TRUE )

## Tidyverse Styling

For **Infix operators** most infix operators (==, +, -, <-, etc.) should always be surrounded by spaces:

*GOOD*

height <- (feet * 12) + inches

mean(x, na.rm = TRUE)

*Suboptimal*

height<-feet*12+inches

mean(x, na.rm=TRUE)

## Tidyverse Styling

For **long lines** use indentation. 80 characters per line. Do one function on each line.

*Good*

```{r}
#do_something_very_complicated(
#  something = "that",
#  requires = many,
#  arguments = "some of which may be long"
#)
```

*Suboptimal*

```{r}
#do_something_very_complicated("that", requires, many, arguments,
#                              "some of which may be long"
#                              )

#do_something_very_complicated(something = "that", requires = many, arguments =
#"some of which may be long")                              

```


