---
title: "Penguins Lab"
author: "Insert Student Name"
date: "Insert Date"
output: html_document
---

#### Objectives
- Connect to Github to retrieve this script
- Pull an update to the script
- The object orientation of R
- Functions & Arguments
- Different types of values: numeric vs. character
- Simple data manipulation
- Graphing
- Statistical tests
- There is always more than one way to do things
- Knit final result into a PDF

#### Loading Libraries 

```{r, message=FALSE, include=TRUE}
library(tidyverse)
library(palmerpenguins)
```

#### Looking at the data. View your dataset, find your column names, and find the dimensions of the dataset.

For the purposes of Knitting this document afterwards, please use the View command, both in the console and in a chunk. Once you have used it in a chunk, try commenting it out. Remember your "#."

```{r}
#View(penguins)

dim(penguins)

colnames(penguins)

#OR

#penguins %>% 
  #View()

penguins %>% 
  dim()

penguins %>% 
  colnames()

```

#### What kind of variable is species?  And bill length? Use the class function and don't forget your $ unless using the pipe operator!

*Insert explanation here*

```{r}
class(penguins$species)

class(penguins$bill_length_mm)

#OR 

penguins$species %>% 
  class()

penguins$bill_length_mm %>% 
  class()
```


#### Filter the gentoo and adelie species, and put it in a new dataset called `two_species`.

```{r}
two_species <- filter(penguins, species == "Adelie" | species == "Gentoo")

#OR 

two_species <- penguins %>% 
  filter(species == "Adelie" | species == "Gentoo")
```

#### Make a box plot using your new two_species set looking at the differences between bill length of the two species of penguin. Add color based on the two species! Explain and interpret this plot.

*Insert explanation here*

```{r, warning=FALSE}
boxplot(bill_length_mm ~ species, data = two_species) 

ggplot(two_species, 
        aes(x = species, y = bill_length_mm, fill = species)) +
        geom_boxplot()

#OR 

two_species %>% 
  ggplot(
    aes(x = species, y = bill_length_mm, fill = species)) + 
    geom_boxplot()
```

#### Run a t-test and a linear regression to see if there is a significant difference between the two species bill length averages. Hint use bill_length_mm for your dependent variable and species as your independent variable. 

*Insert explanation of t-test and model here*

```{r}
t.test(bill_length_mm ~ species, data = two_species)

mod_0 <- lm(bill_length_mm ~ species, data = two_species)

summary(mod_0)
```

#### Knit your final result into a pdf for your own reference and to learn how to create an assignment that could be turned in for future homework.