---
title: "GGPlot Slides"
author: "Melina Much, Ph.D. Candidate"
date: "8/23/2021"
output:
  ioslides_presentation:
    widescreen: true
    smaller: true
---

## Why are we plotting?

Plots are an intuitve way to explore trends in your data, and gain your bearings before starting statistical analysis. It also is an invaluable tool for representing your results to others in papers and presentations. 

## GGplot: What is it?

- Package for creating visualizations based on the "Grammar of Graphics"
- Part of the tidyverse

## GGplot Basic Intuition

It is a three part process that includes:

- Specifying Data
- Mapping Aesthetics
- Adding a Geometric Layer

## Titanic Data

```{r}
library(tidyverse)
library(palmerpenguins)
glimpse(penguins)
```

## Step 1 

Add your data layer.

```{r}
ggplot(data = penguins)
```

## Step 2

Add an aesthetic layer. We are adding an x-axis here. 

```{r}
ggplot(data = penguins,
       aes(x = species))
```

## Step 3 

Add your geometric layer. We are creating a bar plot for the different penguin species! NOTE! The geometric layer is outside of the parenthesis. It is added outside with an addition sign.

```{r}
ggplot(data = penguins,
       aes(x = species)) + 
        geom_bar()
```

## Plain English Explanation

- Create a ggplot using the penguins data frame.
- Map the species to the x-axis.
- Add a layer of a bar plot.

## Example with Continuous Variable

```{r}
ggplot(data = penguins,
       aes(x = flipper_length_mm)) + 
        geom_histogram()
```

## What if we wanted to use a pipe?

```{r}
#Note the warning!
penguins %>% 
ggplot(aes(x = flipper_length_mm)) + 
        geom_histogram()
```

## Lets play with color! 

Color and pipes! We can do it all. You can find more colors [here](http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf).

```{r}
penguins %>% 
ggplot(aes(x = species, fill = species)) + 
        geom_bar()
```

## Two Variable Visualization - Categorical 

Lets make two. 

The first is our standard bar chart, and lets add color for which island the penguin is from. 

```{r}
penguins %>% 
ggplot(aes(x = species, fill = island)) + 
        geom_bar()
```
## Cont. 

The second, we will make a standardized bar chart, which makes the total bar be out of 1. This allows us to look at proportions easily!

```{r}
penguins %>% 
ggplot(aes(x = species, fill = island)) + 
        geom_bar(position = "fill")
```

## Two Variables - Continuous & Categorical

Lets look at bill length and species!

```{r}

penguins %>% 
ggplot(aes(x = species,
           y = bill_length_mm, fill = species))  +
  geom_violin()

```

## Two Variables - All Continuous Numeric!

Lets look at bill length and depth!

```{r}
penguins %>% 
ggplot(aes(x = bill_depth_mm,
           y = bill_length_mm))  +
  geom_point()
```

## Three Variables! Wow!

Note we are adding a color argument as a third variable (species).

```{r}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           color = species)) +
  geom_point()
```

## Hmmm...Can we use something other than dots?

```{r}
penguins %>% 
ggplot(aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point()
```
## Lets make it *really* easy!

We want to start you off with mosaiac as well. While we feel confident in your ability to learn GGplot code, we also want you to have an intuitive way to get yourself started in your own projects. 

Mosaic does just that. It provides a point and click interface to select variables and kinds of plots, while also returning ggplot code so you can see what it did. 

```{r}
#library(mosaic)

#mplot(penguins)

```


