---
title: "Ideology Example"
author: "Melina Much & Kyle McWagner"
output: html_document
---

```{r, include=FALSE}
# Libraries
library(pander)
library(mosaic)
library(tidyverse)
```

```{r, include=FALSE}
# Read in Your Data 

```

### Motivation
In the US political party and political ideology are thought to be very closely connected. Thoe who are more conservative are usually Republicans, and those that are more liberal are usually Democrats. Just because this is true on average, it doesn't mean that it is true for all groups.

### Research Question: 

**Does distribution of party ID and ideology look different for men and women?**

Say we wanted to explore the relationship between partisanship and gender, and ideology and gender. We could make boxplots to look at this relationship.

## Data Exploration

Another common way to look at data is through crosstabs! Crosstabs are tables with counts or percetages for different values of a variable.

# Gender x Party ID

```{r, echo=FALSE}

pander(prop.table(table(cces_2016$gender, cces_2016$partyid)))

```

# Gender x Ideology

```{r, echo=FALSE}
pander(prop.table(table(d1$gender, d1$ideology)))
```

Judging by the tables there does not seem to be a strong association between gender and party ID or ideology. The distribution across the two tables looks similar in many ways. Can you name some ways they are similar?

To get a better sense of how these variables are associated box plots were made using the same variables.

```{r, warning = FALSE, echo=FALSE}

ggplot(data = cces_2016, aes(x = gender, y = partyid)) +
  geom_boxplot()  +
  theme(legend.position = "right") +
  labs(title = "")

ggplot(data = cces_2016, aes(x = gender, y = ideology)) +
  geom_boxplot()  +
  theme(legend.position = "right") +
  labs(title = "")

# Pipe Version

cces_2016 %>% 
  ggplot(aes(x = gender, y = partyid)) +
  geom_boxplot()  +
  theme(legend.position = "right") +
  labs(title = "") 

cces_2016 %>% 
ggplot(aes(x = gender, y = ideology)) +
  geom_boxplot()  +
  theme(legend.position = "right") +
  labs(title = "")

```

Interestingly the box plots reveal that while the distribution of ideology is practically identical for men and women, however, women on average seem to drift towards being Democratic more often then not. Men appear to be split evenly between democrats and republicans. 

To get an even more detailed look at the distribution of party id by gender in order to find out what is driving this observed difference density plot is used with females in red and males in blue.

```{r, warning = FALSE, echo=FALSE}
 ggplot( data = d1, aes(x = partyid)) +
  geom_density(adjust = 1.4) +
  aes(colour = female) +
  labs(title = "") +
  theme(legend.position = "right") 
```

The density plot reveals that men and women are pretty close on the Republican side, but many more men than women are independent or are leaners. Women are on the whole more Democratic. 

# Discussion

This exploratory research reveals that while ideology is identically distributed between men and women,  party id is not, with more women identifying as Democrat. This casts some doubt on the strong link that is assumed between party ID and ideology. One might expect equal distributions of men and women in both party ID and ideology, but we found this isn't the case! 






