---
title: "Day 2 Student Version"
author: "Insert Student Name"
output: html_document
---
#### Objectives and Motivation

We are hoping that you both glean something about American politics, while implementing your new graphing tools!

In the US, political party and political ideology are thought to be very closely connected. With people who are more conservative being Republicans, and those that are more liberal being Democrats. Just because the is true on average, doesn't mean that it true for all groups. Lets investigate this!

##### Research Question: 

**Does the distribution of party ID and ideology look different racial groups? Specifically, does the distribution of party ID and ideology differ for those are Black versus those that aren't?**

Load in our packages.

```{r, message=FALSE}
library(pander) # Makes objects like tables look nice when kniting 
library(mosaic) # Along with lots of other helpful things mplot(dataset) will give you an easy graphical interface to get your graphs started.
library(tidyverse) # Gives you the whole Tidyverse including ggplots2
library(gridExtra) # using the grid.arrange(plot.object, plot.object, nrow = 1) function alws you to put ggplots side by side. 
```

# Read in our data

```{r}

```

**Identify your variables of interest for this question. *Use your codebook!* :)**

 

# Data Exploration

**What is the mean of ideology? What does this mean? Insert an explanation below.**

```{r}

```

**What is the median of ideology?**

```{r}

```


**What is the standard deviation of ideology?**

```{r}

```

**Try using the summary() function to look at all of the above for ideology.**

```{r}

```

**Looking at all of these numbers, what can you say about the distribution, center, and spread of ideology?**



# Graphing

**Make a histogram of ideology, does the histogram confirm or refute what you thought ideology looked like based on the numbers?**

```{r}

```


**Make a graph with at least two variables of interest that are relevant to this question.**

*Hint: Box Plots or Violin Plots would be appropriate here.*

```{r}

```

# Perform a T-Test

**We want to see if there is a systematic difference between the distribution of party ID and ideology for Black and Non-Black individuals. Perform the t-tests.**

```{r}

```


# Discussion

**What do we learn form looking at this data in regards to how the Black indaviguals and non-black indaviguals navigat the relatioship between Party ID and political idioligy?**
