---
title: "Penguins Lab"
author: "Mia"
date: "8/17/2021"
output: html_document
---

### Objectives
- Connect to Github to retrieve this script
- Pull an update to the script
- The object orientation of R
- Functions & Arguments
- Different types of values: numeric vs. character
- Simple data manipulation
- Graphing
- Statistical tests
- There is always more than one way to do things

## Base R Versus Libraries

```{r}
library(tidyverse)
library(palmerpenguins)
```

## Looking at the data. View your dataset, find your column names, and find the dimensions of the dataset.

```{r}
View(penguins)

dim(penguins)

colnames(penguins)

#OR

penguins %>% 
  View()

penguins %>% 
  dim()

penguins %>% 
  colnames()

```

## What kind of variable is species?  And bill length? Use the class function and don't forget your $ unless using the pipe operator!

```{r}
class(penguins$species)

class(penguins$bill_length_mm)

#OR 

penguins$species %>% 
  class()

penguins$bill_length_mm %>% 
  class()
```


## Filter the gentoo and adelie species, and put it in a new dataset called `two_species`.

```{r}
two_species <- filter(penguins, species == "Adelie" | species == "Gentoo")

OR 

two_species <- penguins %>% 
  filter(species == "Adelie" | species == "Gentoo")
```

What 
## Looking at raw data

```{r}
#bball

#head(bball)

#View(bball)
```

## Graphing

```{r}
boxplot(points ~ height, data = bball) 

ggplot(bball, 
        aes(x = height, y = points, fill = height)) +
        geom_boxplot()
```

## Statistical tests

```{r}
t.test(points ~ height, data = bball)

mod_0 <- lm(points ~ height, data = bball)

summary(mod_0)
```

