---
title: "Penguins Lab"
author: "Mia"
date: "8/17/2021"
output: html_document
---

### Objectives
- Connect to Github to retrieve this script
- Pull an update to the script
- The object orientation of R
- Functions & Arguments
- Different types of values: numeric vs. character
- Simple data manipulation
- Graphing
- Statistical tests
- There is always more than one way to do things

## Base R Versus Libraries

```{r}
library(tidyverse)
library(palmerpenguins)
```

## Looking at the data. View your dataset, find your column names.

```{r}
View(penguins)

colnames(penguins)
```

## Filter the gentoo and adelie species.

```{r}
filter(penguins, )

OR 

penguins <- penguins %>% 
  filter(species == )
```

## Data manipulation

```{r}
points <- c(point_low, point_high)
```

## Non-numeric objects

```{r}
height <- c("short", "short", "short", "short", "short", "short", "short", 
  "tall", "tall", "tall", "tall", "tall", "tall", "tall") 

height <- c(rep("short", 7), rep("tall", 7))

height <- as.data.frame(height)
```

## Data manipulation
```{r}
bball <- cbind(points, height)
```

## Looking at raw data

```{r}
#bball

#head(bball)

#View(bball)
```

## Graphing

```{r}
boxplot(points ~ height, data = bball) 

ggplot(bball, 
        aes(x = height, y = points, fill = height)) +
        geom_boxplot()
```

## Statistical tests

```{r}
t.test(points ~ height, data = bball)

mod_0 <- lm(points ~ height, data = bball)

summary(mod_0)
```

