---
title: "Penguins  Lab"
author: "Insert Student Name"
date: "Insert Date"
output: html_document
---

#### Objectives
- Connect to Github to retrieve this script
- Pull an update to the script
- The object orientation of R
- Functions & Arguments
- Different types of values: numeric vs. character
- Simple data manipulation
- Graphing
- Statistical tests
- There is always more than one way to do things
- Knit final result into a PDF

#### Loading Libraries 

```{r, message=FALSE, include=TRUE}
library(tidyverse)
library(palmerpenguins)
```

#### Looking at the data. 

View your dataset.

*For the purposes of Knitting this document afterwards, please use the View command, both in the console and in a chunk. Once you have used it in a chunk, try commenting it out. Remember your "#."*

```{r}
#View()
```

Find your column names.
```{r}
```

Find the dimensions of the dataset.
```{r}
```


#### What are the classes of variables?


Use the class function and don't forget your $ unless using the pipe operator!

What kind of variable is species? 

```{r}

```

What kind of variable is bill length? 

```{r}
\
```

*Insert explanation here*


#### Filter the gentoo and adelie species, and put it in a new dataset called `two_species`.

```{r}

```

#### Making Boxplots

Make a box plot using your new two_species set looking at the differences between bill length of the two species of penguin. Add color based on the two species! Explain and interpret this plot.

*Insert explanation here*

```{r, warning=FALSE}

```

#### Run a t-test and a linear regression to see if there is a significant difference between the two species bill length averages. Hint use bill_length_mm for your dependent variable and species as your independent variable. 

*Insert explanation of t-test and model here*

```{r}

```

#### Knit your final result for your own reference and to learn how to create an assignment that could be turned in for future homework.
