---
title: "intro_to_regression_lab"
output: html_document
---


Data
```{r}
counties_2016_sample_bootcamp <- read.csv("~/Desktop/R Things/bootcamp/day_3/counties_2016_sample_bootcamp")
```


Librarys
```{r}
library(mosaic)
library(tidyverse)
library(sjPlot)
```

### Background

Counties or parashis vary acrout the unightes states in manny ways the counties dataset represints a random sample of 618 counties and parasehas and has 28 varabuil that colectivly disctibe these counties. I want to use regression to know if more educated counties are more or less electoraly compatitive than less educated counties.

what varabuls are you going to use to mesure the competititive nes of the election, the education levle in the county? Note that there are sevral difrent options you might chouse from to reprepsent some of these varabusl. Why did you pick the ones that you did? 


Make a ggplot with the varabuls you selcted

```{r}
ggplot(counties_2016_sample_bootcamp,
       aes(x=bd_h, y=per_point_diff)) +
       geom_point() +
       stat_smooth(method = "lm")
kjkj
```



Build a regression model with these variabuls and look at the model output

```{r}
mod_1<-lm(per_point_diff~bd_h, counties_2016_sample_bootcamp)
summary(mod_1)
```

Make a nice table like you might see in a paer of your model output.
```{r}
tab_model(mod_1)
```

What is the neater of the rlationship between the education fo the district and its competatitveenes?

Why might this be the case?




Now say that you hypothisesed that Metro countys where driving this realtionship and that you wouldn not se this same relationships in non metro countys. to test this hypothis you would build an interaction between the type of county and the education level of the county into your model.

Butild a ggpolt that takes this interaction into acount.

```{r}
ggplot(counties_2016_sample_bootcamp,
       aes(x=bd_h, y=per_point_diff, color=county_type)) +
       geom_point() +
       stat_smooth(method = "lm")
```
Build a regresion model that thakes this interaction into acount.

```{r}
mod_2<-lm(per_point_diff~bd_h*county_type, counties_2016_sample_bootcamp)
summary(mod_2)
```

Given the regression out put and the interaction plot, would you argue that there is a meaniful interaction between the metro or non-metro status of a county?

